Outdated and License-Violating Code on Stack Overflow

### 2017-10-12 cloverflow-tse/cloverflow.tex
Fixed the number of QS and outdated clone pairs.

\begin{table}
	\caption{Investigated online clone pairs and corresponding snippets
		and Qualitas projects}
	\label{tab:snippets}
	\centering
	\begin{tabular}{p{2.2cm}rrrr}
		\toprule
		Set & Pairs & Snippets & Projects & Cloned ratio \\
		\midrule
		Reported clones & 2,302 & 460 & 59 & 53.10\% \\ 
		\midrule
		TP from manual validation & 2,076 & 449 & 59 & 54.22\% \\ 
		\bottomrule
	\end{tabular}
\end{table}

During the manual investigation of 2,302 clone pairs, we identified 226 pairs
as being accidental clones (AC), i.e.~false positives. After removing
them, the set still contains 2,076 true positive clone pairs between 449 Stack
Overflow snippets and 59 Qualitas projects. The average cloned ratio for the
true positive clone pairs is 54.22\%.

\textbf{To answer RQ1, we found more than half of Qualitas projects to share
	similar code with Stack Overflow code snippets. In the manually confirmed 
	data set of 2,302 clone pairs, we found 2,076 pairs as true positives which 
	account for 59 Qualitas projects and
	449 Stack Overflow code snippets.}

@@

\begin{table}
	\centering
	\caption{Six code modification types found when comparing the outdated clone pairs to their latest versions}
	\label{tab:mod_types}
		\begin{tabular}{lr}
			\toprule
			Modification & Occurrences \\
			\midrule
			Statement modification & 49 \\
			Statement addition & 29 \\
			Statement removal & 18 \\
			Method signature change & 16 \\
			Method rewriting & 15 \\
			File deletion & 15 \\
			\bottomrule 
		\end{tabular}
\end{table}

>>>>

\begin{table}
	\caption{Investigated online clone pairs and corresponding snippets
		and Qualitas projects}
	\label{tab:snippets}
	\centering
	\begin{tabular}{p{2.2cm}rrrr}
		\toprule
		Set & Pairs & Snippets & Projects & Cloned ratio \\
		\midrule
		Reported clones & 2,302 & 460 & 59 & 53.10\% \\ 
		\midrule
		TP from manual validation & 2,076 & 443 & 59 & 53.89\% \\ 
		\bottomrule
	\end{tabular}
\end{table}

During the manual investigation of 2,302 clone pairs, we identified 226 pairs
as being accidental clones (AC), i.e.~false positives. After removing
them, the set still contains 2,076 true positive clone pairs between 443 Stack
Overflow snippets and 59 Qualitas projects. The average cloned ratio for the
true positive clone pairs is 53.89\%.

\textbf{To answer RQ1, we found more than half of Qualitas projects to share
	similar code with Stack Overflow code snippets. In the manually confirmed 
	data set of 2,302 clone pairs, we found 2,076 pairs as true positives which 
	account for 59 Qualitas projects and
	443 Stack Overflow code snippets.}

@@

\begin{table}
	\centering
	\caption{Six code modification types found when comparing the outdated clone pairs to their latest versions}
	\label{tab:mod_types}
		\begin{tabular}{lr}
			\toprule
			Modification & Occurrences \\
			\midrule
			Statement modification & 50 \\
			Statement addition & 28 \\
			Statement removal & 18 \\
			Method signature change & 16 \\
			Method rewriting & 15 \\
			File deletion & 15 \\
			\bottomrule 
		\end{tabular}
\end{table}
